Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex

>>>>

The nucleon tensor charge is a fundamental property of the nucleon and is at
present poorly constrained. Several estimates based on lattice
QCD are available, but only limited information from direct measurements. The
way to extract the tensor charge from experimental measurements requires first
the extraction the so-called transversity parton distribution function (PDF),
denoted by $h_1^q(x)$. The transversity distribution is then integrated over
$x$ to yield the contribution of flavor $q$ to tensor charge.

In this paper, we discuss the possibility of observing the effect of
the transversity distribution in totally inclusive Deep Inelastic Scattering.

The transversity distribution is notoriously difficult to access because it is
a chiral-odd function and needs to be combined with a spin-flip mechanism to
appear in a scattering process. Usually, this spin flip is provided by another
nonperturbative distribution or fragmentation function, implying that
transversity cannot be accessed in inclusive DIS,
but only in more complex processes such as semi-inclusive DIS or Drell-Yan.

The only other way to attain spin-flip terms in QED and QCD is taking into
account mass corrections. In fact, it is well known that transversity gives a
contribution to the structure function $g_2$ in inclusive DIS, and in
particular to the violation of the so-called Wandzura--Wilczek relation for
$g_2$. However, this contribution is proportional to the current quark mass
and can be expected to be very small.

We revisit the standard analysis of inclusive DIS taking into account the fact
that on-shell quarks cannot be present in the final state, but they rather
decay into hadrons (ideally, the form jets of hadrons). This is sufficient to modify the structure of the DIS
cut-diagram, even if none of the hadrons is detected in the final
state. For a proper description of this effect, we include ``jet
correlators'' into the analysis. We pay particular attention to insuring that our
results are gauge invariant. We observe that the inclusion of jet correlators
introduces a new
contribution to the inclusive $g_2$ structure function. This term has the
interesting features that: a) violates the Wandzura--Wilczek relation, b)
violates the Burkhardt--Cottingham sum rule, c) is
proportional to the transversity distribution function multiplied by a
nonperturbative ``jet mass'' parameter. We provide estimates of this
contribution based on a recent extraction of transversity and show that it
could be very large.
